Spherical harmonic analysis of faceted spheroids identifies shaping strategies and standardisation at Qianshangying (North China)

### 2025-08-22 analysis/paper/paper.qmd

# KMeans clustering (k=4)
set.seed(123)
kmeans_result <- kmeans(umap_data[, c("x", "y")], centers = 4)

>>>>

# Elbow method for optimal K
wss <- numeric(10)

for (k in 1:10) {
  set.seed(123)  
  km <- kmeans(umap_data[, c("x", "y")], centers = k)
  wss[k] <- km$tot.withinss  
}

elbow_test <-
  plot(1:10, wss, type="b", pch=19, frame=FALSE,
       xlab="Number of clusters K",
       ylab="Total within-cluster sum of squares (WSS)",
       main="Elbow Method for Optimal K")

# KMeans clustering (k=4)
set.seed(123)
kmeans_result <- kmeans(umap_data[, c("x", "y")], centers = 3)
